Vulnerability Analysis of Container Images in Neuroimaging

### 2020-06-23 paper.tex
structure modification 1

\title{Vulnerability Analysis of Container Images in Neuroimaging}

@@

\begin{keywords}
Containers; Vulnerabilities; Docker; Singularity; Neuroimaging.
\end{keywords}

@@

Containers, which provide an operating system (OS) level virtualization, are
popular. This is because they are lightweight, flexible, resource-efficient,
provide fast development cycles, continuous delivery,
and cost reduction of infrastructure. OS-level virtualization gained a lot of interest when Docker~\cite{docker19} was
introduced in 2013~\cite{gantikow2016providing}. However, Docker has security concerns due to which it
is not supported by High Performance
Computing (HPC) environments. As a result, Singularity~\cite{singularity19} came in 2016 with the goal of providing support
for HPC environments. It is used in many clusters including Compute Canada.
According to~\cite{kurtzer2017singularity}, Singularity is used in 36 research clusters.

@@

No doubt containers have gained a lot of popularity, however containers tightly
integrate with the host due to the sharing of the kernel, 
mounted file systems, and devices, which raises security
concerns.
They also share three main security threats with other virtualization
techniques~\cite{gantikow2016providing}:

\begin{comment}
\begin{figure}
  \centering
  \includegraphics[width=.7\columnwidth]{Figures/container.png}
  \caption{Architecture of Container-based
                Virtualization.}
  \label{fig:container-overview}
\end{figure}
\end{comment}
\textit{Privilege Escalation} A malicious attacker can break out of the container
and gain control of the host system and other containers running on the same host.

\textit{Denial-of-Service} One container may end up eating all the resources of the
host hence resulting in the starvation of the host and other containers.

@@

However, two features of the Linux kernel, \textit{control groups} and \textit{namespaces},
are used by containers to mitigate these threats to a certain extent. The security
of containers is still the most concerning issue. According to a Forrester survey~\cite{bettini2015vulnerability}
done in January 2015, security is the
biggest concern while deploying containers.
Containers are popular in various scientific fields, in particular to run Big Data analyses
on HPC clusters. 
However, deploying Docker container images on clusters raises security issues. Some security issues 
that could possibly lead to privilege escalation, DoS or information leak. Some
security issues are related to the architecture of Docker but have been 
largely solved by Singularity.
In fact, Singularity was developed for scientific applications
by keeping the focus on HPC environments. Although, this work is of general interest,
our particular focus in this paper is neuroimaging as containers are popularly used for scientific computing and data science
in neuroscience.
This popularity of containers in neuroscience leads us to the
primary research question of this work: \textit{what is the current security state of
neuroimaging container images that are deployed on HPC clusters?}

To answer that question, we scan images that are used on Compute
Canada clusters by the Neuroscience field. Scanning refers to the practice of
collecting all information about the container image, investigating it
for vulnerabilities, and finally producing a
report to summarize scanning results. It is broadly categorized into
two types: Static scanning and Dynamic scanning. The former scanning technique
involves extracting information of an image without running it into a container,
whereas the latter approach involves launching the container from the target image, and
then scanning the running container.
Here, we focus mainly on vulnerability scanning.
Vulnerability is a weakness in the developer's software that can be exploited
by the attacker to perform unauthorized actions on the target computer.
In this paper, we report vulnerabilities that are present in
container images, specifically used by neuroimaging field. Particularly,
we aim to answer four primary research questions:

\textit{RQ1:} Are vulnerabilities present inside neuroimaging container images that are
deployed on HPC clusters?

\textit{RQ2:} Can these vulnerabilities be reduced by updating the images?

\textit{RQ3:} Can these vulnerabilities be reduced by shrinking the size of the images?

@@

The existing research work on containers focuses mainly on the security of Docker
containers.
This focus is justified by the fact that containers expose the host's resources
(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
threat for the applications running on the same host. Previous studies evaluated
the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
Zerouali et al. in~\cite{zerouali2019relation} studied severity vulnerabilities and bugs in Docker 
containers due to outdated packages.

There are various image scanners available for scanning Docker images, for
instance Anchore, CoreOS's Clair, etc.
However, these scanners cannot be used to scan Singularity images due to different image formats.
Therefore, Singularity came up with Stools~\cite{stools}, which can be used for scanning Singularity images
for security and quality checks.

This paper is organized as follows: in the next section, we provide description
of materials and methods which summarize our experiments. We also explain different
image scanners used to report
vulnerabilities in container images. The next section of this paper provides the results, where we
present a number of existing vulnerabilities in the container images
used for data analysis on shared HPC clusters. We then proceed in the following section with 
discussion and analysis of these results, where we provide more insight into the problems that 
we faced while conducting these experiments. We also propose some
particular rules that can be followed to secure container images. Finally, conclusions are drawn
in the last section of the paper.

\section{Materials and Methods}

This study involves several image scanning experiments. To begin with,
we scan the images as is to report the vulnerabilities
inside the images. Updating and shrinking the size of these images is likely to play a role in vulnerabilities. Therefore, we
update the images and then rescan all these
images.
Subsequently, we shrink the size of the images
meaning that remove unnecessary packages from the images to see the effect on the number of
vulnerabilities in the images.
Lastly, we update and shrink the image size together and then
rescan for the vulnerabilities.

In this section, we provide
insight
into the container images and the image scanners that we used in our study.
The image scanners refer to different Linux
distributions/releases, which have different vulnerability data and is likely to
create discrepancies in results. Therefore, in the last, this section presents a
description of these varying Linux distributions/releases and their
vulnerability databases.

%As we are taking a particular use case of containers from
%neuroscience field i.e Canadian Open Neuroscoence Platform (CONP) so  
%in this section we summarize the data and tools 
%that are used in CONP. CONP is a national platform for sharing neuroscience
%research data and aims at creating an interactive interface for neuroscientists and
%clinical neuroscience. The main goal of the CONP platform is to store, process, and
%distribute massive amounts of data produced by modern neuroscience.
%Here, we summarize all the resources that are
%used by CONP to function.

@@

%\begin{comment}
%Singularity offers mobility of compute by facilitating portable environments 
%through a single image file~\cite{kurtzer2017singularity}. Once Singularity image
%is created, it is hashed using SHA-256. Hence, it cannot be changed
%once it is created, consequently, it can be used for reproducing the results of
%scientific experiments. Main features provided by
%Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
%We used Singularity version $2.5.2$ in our experiments.
%Users can easily access files, devices, sockets, ports of the host system from
%the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
%into the running container. Additional directories can be specified with \textit{--bind}
%to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
%However namespaces can be requested if required. Users cannot escalate privileges inside
%Singularty containers. This is because Singularity do not run containers as root.
%Instead, a user inside Singularity container is the same user outside the container.
%
%\subsection{Container Image Formats}
%
%A container image is a package that contains an application along with its
%required dependencies and libraries.
%Both, Docker and Singularity, have different image formats. Below we provide a description of both image
%formats.
%
%\subsubsection{Docker Image Format}
%
%Docker images are organized as a series of layers stacked on top of each
%other and identified by unique layer identifiers. If a layer is reused
%in different images it will
%have the same id across images. Each layer consists of a filesystem diff
%with respect to the layer below. 
%DockerHub uses gzip compression for
%transferring layers.There are two ways to create a Docker image. The
%first is to use an existing Docker image as a base image and then build a
%new image from that one, by making changes in the filesystem, which is
%saved as a new layer of the Docker image. The second way is to build a new
%Docker image from scratch.Docker supports several different storage drivers.
%\textit{Overlay2} is the preferred storage driver used by Docker for all currently
%supported Linux versions, whereas \textit{aufs} is preferred for Docker 18.06 and
%older, when using Ubuntu 14.04 on kernel 3.13 as it do not support \textit{overlay2}.
%Other storage drivers that are supported by Docker include \textit{devicemapper, btrfs,
%zfs, and vfs}
%
%\subsubsection{Singularity Image Format}
%
%On the other hand, a Singularity image is a single immutable file and 
%does not contain layers.
%Once a Singularity image is created, it cannot be changed, consequently,
%it can be used for reproducing the results of scientific
%experiments.
%Singularity takes snapshot, locks, and archives the developed application,
%which is known as Singularity image.
%It means that Singularity image is a single immutable file that can be moved around as
%any other file. This file can be checksummed, signed, and easily
%used for verification purposes. Singularity containers use Squashfs file format
%by default. It is read-only file system in Linux, which uses compression for files,
%inodes, and directories. However, Singularity also supports two other 
%formats i.e \textit{sandbox} format
%(which is just a chroot
%directory) and \textit{writable} format (the ext3 file system).
%While publishing experimental results, authors can also publish Singularity
%image along with its hash, which allow other researchers to verify results.
%\end{comment}
\subsection{Container images}

We scan a total of 44 container images taken from the BIDS
apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}
frameworks, two containerization frameworks used in neuroscience to share
and re-use applications. Among the 27 BIDS apps \href{https://bids-apps.neuroimaging.io/apps/}
{(https://bids-apps.neuroimaging.io/apps/)} available at the time of
the study, we studied 26
unique Docker images as one wasn't available on DockerHub. Among the 49
Boutiques applications available at the time of the study, listed using
Boutiques \texttt{bosh search} command, 23 unique container images were
listed including 3 that couldn't be retrieved and 2 that were already
included in BIDS apps. The resulting 18 images included 12 Docker images
and 6 Singularity images.
%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

@@

We used four popular image scanners, namely Anchore~\cite{github_2019},
Vuls~\cite{future-architect_2019}, Clair Scanner~\cite{arminc_2019} and
Stools~\cite{stools}. Anchore, Vuls and Clair Scanner support Docker
images while Stools supports Singularity. 
To avoid discrepancies, we froze the vulnerability
databases for these scanners on September 25, 2019.

@@

Anchore is an end-to-end, open-source container security platform. It
is a static
scanning tool that analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
%\begin{comment}
%Anchore is a set of tools, which users can
%employ for scanning container images and applying custom policies to them.
%It provides visibility and transparency of the container environment.
%\end{comment}
Anchore Engine can be used in two ways: through Docker image or Anchore
Command Line Interface (CLI).
%\begin{comment}
%Anchore offers services in two ways: Anchore Engine and Anchore
%Command Line Interface (CLI). Anchore Engine is available as a Docker
%image, which is available on Docker Hub. Anchore Engine CLI provides
%command line interface in addition to Anchore Engine REST API. 
%\end{comment}
It can be
installed directly on the host and used to inspect images.
In our experiments, we used a Docker image to get Anchore Engine version 0.5.0 and Database
version 0.0.11.

Anchore compares package versions, which are present inside the
image, with the vulnerability database in order to flag vulnerabilities.
To get a vulnerability feed of various OS distribution, Anchore refers to
different sources. For example, the Ubuntu launchpad database is used for Ubuntu.

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
It offers both static and dynamic scanning. In our experiments, we used
it to dynamically scan containers.
Using a dynamic scanning technique, it offers
remote and local scans at the time of writing. The remote scan involves setting up only one machine, to
which other target servers are connected via SSH. Local scan involves running
the scan on the target server itself. Further, Vuls offer a fast scan, fast root scan,
and deep scan mode.
%The Fast scan is performed without root privileges, whereas a fast root scan is
%performed with root privileges. The latter also uses checkrestart utility to 
%detect processes that are updated but not yet restarted because if they are not
%restarted, updates are not effective. Fast root scan also detects these
%processes. Both fast scan and fast root scan are performed offline without Internet
%access, and put almost no load on the scan target server. The Deep scan uses
%root privileges for scanning and is used to get a more detailed scan. It checks
%changelogs, which puts more load on the target server.

In our experiments, we used Vuls Docker image having version 0.9.0 with fast scan mode.
Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
The interesting point is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
meaning that images with these distributions are hard to scan with Vuls.

\subsubsection{Clair Scanner}

CoreOS originally created Clair, a static vulnerability scanner for containers. 
\begin{comment}
The main goal of the
tool is to provide a transparent look of container’s security. Clair scans container images in regular
intervals, and stores metadata of vulnerabilities, after getting from configured
set of sources. 
\end{comment}	
Clair API can be used by clients to query its database to get
the list of vulnerabilities that a particular image has. Clair sends a notification
to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
is a registry to store images privately, uses Clair internally as the security engine. However, Clair does not 
provide the facility for comparing
the vulnerability list of a particular image against a whitelist of vulnerabilities that you
want to ignore~\cite{arminc_2019}. 
So, to remove
that drawback, another tool from CoreOS, Clair Scanner can be used. It scans the image, prepares the list of
vulnerabilities, compares that list against a whitelist, and flags vulnerabilities
that are not present in the whitelist.
Clair Scanner refers to the Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
For that purpose, a Docker image is maintained that contains the Ubuntu CVE tracker database.
Whenever Ubuntu updates its database, this image is also updated with the required information.

In our experiments, we used a Docker image (arminc/clair-local-scan:v2.0.6) for scanning
and an another Docker image (arminc/clair-db:latest) for the vulnerability database, which was
last updated on 2019-09-18. We performed
scanning on 2019-09-25. So, it means that Clair Scanner's database was already
old by one week.

@@

Stools combines CoreOS's Clair Scanner with Continuous Integration (CI)
for scanning Singularity images for vulnerabilities.
Initially, Clair Scanner was intended to scan Docker images only. This tool does not fit well
to scan Singularity images because of the different image formats.
However, TravisCI and CircleCI are commonly used for testing code, and these
services also offer running containers. Stools combined both these concepts.
It involves spinning a Clair Scanner container during testing and building a
Singularity image, and scanning it for filesystem before the image is finalized.

In our experiments, we used a Docker image (\href{https://hub.docker.com/r/vanessa/stools-clair}{vanessa/stools-clair:v3.2.1})
for scanning and followed the steps mentioned in \href{https://github.com/singularityhub/stools}{Stools Github}.

@@

\subsection{Image Update and Reduction Process}

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script 
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/update/update.sh}{Github}) 
to update all images, which checks the
package manager present inside the image and then according to that it
updates the image. However, this option affects the reproducibility
of the image, which means that the image cannot be used to verify the research
findings of other scientists.

>>>>

\renewcommand{\labelitemi}{$\textendash$}
\title{Vulnerability Analysis of Container Images in Neuroimaging}

@@

\begin{keywords}
Containers; Docker; Singularity; Security; Vulnerabilities; Image Scanning; Outdated packages; Shrinking Images; Neuroimaging.
\end{keywords}

@@

Containers, which provide an operating system (OS) level virtualization, are
popular. This is due to them being lightweight, flexible, and resource-efficient.
Additionally, they are capable of providing fast development cycles and continuous delivery with the
reduction of infrastructure cost~\cite{martin2018docker}. Containers are heavily utilised in various scientific fields,
in particular, to run big data analysis. OS-level virtualization gained a lot of interest when Docker~\cite{docker19} was
introduced in 2013. However, Docker is not supported by High Performance Computing (HPC)
environments, mainly due to the fact that Docker user can act as superuser inside the container.
As a result, Singularity~\cite{singularity19} was developed
for scientific applications by keeping the focus on HPC environments. In addition, Singularity also solves some other security issues
related to the architecture of Docker. It is used in many clusters including Compute Canada.
According to~\cite{kurtzer2017singularity}, Singularity is used in 36 research clusters.

@@

Inspite of their popularity, containers tightly
integrate with the host due to the sharing of the kernel, 
mounted file systems, and devices, which raises security
concerns.
In fact, in relation to other virtualization techniques, they share three main security threats~\cite{gantikow2016providing}:

\begin{comment}
\begin{figure}
  \centering
  \includegraphics[width=.7\columnwidth]{Figures/container.png}
  \caption{Architecture of Container-based
                Virtualization.}
  \label{fig:container-overview}
\end{figure}
\end{comment}
\textit{Privilege Escalation} A malicious attacker can break out of the container
and gain control of the host system and other containers running on the same host;

\textit{Denial-of-Service} One container may end up consuming all the resources of the
host, hence resulting in the starvation of the host and other containers;

@@

In order to mitigate these threats, containers use some features of the Linux kernel
such as \textit{control groups, namespaces}, etc. For instance, \textit{control groups}
are used to restrict the amount of resources that a container can use. Nonetheless, container's
security is still one of the concerning issues.
%However, two features of the Linux kernel, \textit{control groups} and \textit{namespaces},
%are used by containers to mitigate these threats to a certain extent. The security
%of containers is still the most concerning issue. 
According to a 2015 Forrester survey, security is the
biggest concern when deploying containers~\cite{bettini2015vulnerability}.
%Containers are popular in various scientific fields, in particular to run Big Data analyses
%on HPC clusters. 
%However, deploying Docker container images on clusters raises security issues. Some security issues 
%that could possibly lead to privilege escalation, DoS or information leak. Some
%Above mentioned threats are not the only security issues that containers may suffer.
%Other security issues are related to the architecture of Docker but have been 
%largely solved by Singularity.
%In fact, Singularity was developed for scientific applications
%by keeping the focus on HPC environments. Although, this work is of general interest,
%our particular focus in this paper is neuroimaging as containers are popularly used for scientific computing and data science
%in neuroscience.
While containers still suffer general security problems that may affect any application using
them, our particular focus in this research is the security of container images.
In this research work, we aim to study and analyse the security of container images.
Although this work, is of general interest and can be applied on any field, we focus in this
paper on neuroimaging. This is due to the fact that containers are particulary popular in
scientific computing and heavily utiilised in neuroscience, which makes it a good candidate
for this research.
This popularity of containers in neuroscience leads us to the following
primary research question:

\textit{RQ1: What is the current security state of
neuroscience container images that are deployed on HPC clusters?}

In fact, answering this question leads us to further questions as described below. 
To answer our primary research question, we scan neuroscience images. The purpose
of this scanning process is to collect information about the container images
and then investigate these findings against security vulnerabilities.
%we scan images that are used on Compute
%Canada clusters by the Neuroscience field. Scanning refers to the practice of
%collecting all information about the container image, investigating it
%for vulnerabilities, and finally producing a
%report to summarize scanning results. 
It is broadly categorized into
two types: \textit{Static} and \textit{Dynamic} scanning. The former
involves extracting information of an image without running that image into a container,
whereas the latter involves running a container with the target image.
While scanning may provide different information, here, we focus mainly on security vulnerability.
These types of vulnerabilities may be caused by an exploitable weakness in developer's software.
Such exploitation may result in serious attacks such as gaining unauthorized access on the target
computer, deletion of mounted files, etc. In this work, we target the detection of vulnerabilities
that are present in neuroscience container images. It is further important to answer following three 
secondary questions:
%Vulnerability is a weakness in the developer's software that can be exploited
%by the attacker to perform unauthorized actions on the target computer.
%In this paper, we report vulnerabilities that are present in
%container images, specifically used by neuroimaging field. Particularly,
%we aim to answer four primary research questions:

\textit{RQ2:} Can vulnerabilities be reduced by updating the images?

\textit{RQ3:} Can vulnerabilities be reduced by shrinking the size of the images?

@@

%%%%%%%%%Related Work%%%%%%%
%The existing research work on containers focuses mainly on the security of Docker
%containers.
%This focus is justified by the fact that containers expose the host's resources
%(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
%threat for the applications running on the same host. Previous studies evaluated
%the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
%and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
%Zerouali et al. in~\cite{zerouali2019relation} studied severity vulnerabilities and bugs in Docker 
%containers due to outdated packages. 
%
%There are various image scanners available for scanning Docker images, for
%instance Anchore, CoreOS's Clair, etc.
%However, these scanners cannot be used to scan Singularity images due to different image formats.
%Therefore, Singularity came up with Stools~\cite{stools}, which can be used for scanning Singularity images
%for security and quality checks.

This paper is organized as follows: in the next section, we provide a description
of materials and tools, which we utilise throughout our experiments. We also present
different image scanners used for vulnerability reporting in container images.
The following section of this paper provides our approach and methodology, where we
mainly examine the effect of image update and image reduction for the purpose
of reducing vulnerabilities. Afterwards, we provide the results of our experiments,
where we indicate a number of detected vulnerabilities in container images used for
data analysis on shared HPC clusters. The last two sections provide a conclusion of this
work following by a summary and an indication of our future work.

%This paper is organized as follows: in the next section, we provide a description
%of materials and methods which summarize our experiments. We also explain different
%image scanners used to report
%vulnerabilities in container images. The next section of this paper provides the results, where we
%present a number of existing vulnerabilities in the container images
%used for data analysis on shared HPC clusters. We then proceed in the following section with 
%discussion and analysis of these results, where we provide more insight into the problems that 
%we faced while conducting these experiments. We also propose some
%particular rules that can be followed to secure container images. Finally, conclusions are drawn
%in the last section of the paper.

\section{Materials and Tools}

Since the aim of this reseach work is to detect security vulnerabilities
in container images and attempt to examine the effect of different
manipulation of these images, it is needed to have sufficient number of
images. Additionally, for the purpose of detecting vulnerabilities,
utilization of image scanners is required. We utilize container
images from two different containerization frameworks as well as
various image scanners tools.

%This study involves several image scanning experiments. To begin with,
%we scan the images as is to report the vulnerabilities
%inside the images. Updating and shrinking the size of these images is likely to play a role in vulnerabilities. Therefore, we
%update the images and then rescan all these
%images.
%Subsequently, we shrink the size of the images
%meaning that remove unnecessary packages from the images to see the effect on the number of
%vulnerabilities in the images.
%Lastly, we update and shrink the image size together and then
%rescan for the vulnerabilities.
%
%In this section, we provide
%insight
%into the container images and the image scanners that we used in our study.
%The image scanners refer to different Linux
%distributions/releases, which have different vulnerability data and is likely to
%create discrepancies in results. Therefore, in the last, this section presents a
%description of these varying Linux distributions/releases and their
%vulnerability databases.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%As we are taking a particular use case of containers from
%neuroscience field i.e Canadian Open Neuroscoence Platform (CONP) so  
%in this section we summarize the data and tools 
%that are used in CONP. CONP is a national platform for sharing neuroscience
%research data and aims at creating an interactive interface for neuroscientists and
%clinical neuroscience. The main goal of the CONP platform is to store, process, and
%distribute massive amounts of data produced by modern neuroscience.
%Here, we summarize all the resources that are
%used by CONP to function.

@@

%\begin{comment}
%Singularity offers mobility of compute by facilitating portable environments 
%through a single image file~\cite{kurtzer2017singularity}. Once Singularity image
%is created, it is hashed using SHA-256. Hence, it cannot be changed
%once it is created, consequently, it can be used for reproducing the results of
%scientific experiments. Main features provided by
%Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
%We used Singularity version $2.5.2$ in our experiments.
%Users can easily access files, devices, sockets, ports of the host system from
%the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
%into the running container. Additional directories can be specified with \textit{--bind}
%to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
%However namespaces can be requested if required. Users cannot escalate privileges inside
%Singularty containers. This is because Singularity do not run containers as root.
%Instead, a user inside Singularity container is the same user outside the container.
%
%\subsection{Container Image Formats}
%
%A container image is a package that contains an application along with its
%required dependencies and libraries.
%Both, Docker and Singularity, have different image formats. Below we provide a description of both image
%formats.
%
%\subsubsection{Docker Image Format}
%
%Docker images are organized as a series of layers stacked on top of each
%other and identified by unique layer identifiers. If a layer is reused
%in different images it will
%have the same id across images. Each layer consists of a filesystem diff
%with respect to the layer below. 
%DockerHub uses gzip compression for
%transferring layers.There are two ways to create a Docker image. The
%first is to use an existing Docker image as a base image and then build a
%new image from that one, by making changes in the filesystem, which is
%saved as a new layer of the Docker image. The second way is to build a new
%Docker image from scratch.Docker supports several different storage drivers.
%\textit{Overlay2} is the preferred storage driver used by Docker for all currently
%supported Linux versions, whereas \textit{aufs} is preferred for Docker 18.06 and
%older, when using Ubuntu 14.04 on kernel 3.13 as it do not support \textit{overlay2}.
%Other storage drivers that are supported by Docker include \textit{devicemapper, btrfs,
%zfs, and vfs}
%
%\subsubsection{Singularity Image Format}
%
%On the other hand, a Singularity image is a single immutable file and 
%does not contain layers.
%Once a Singularity image is created, it cannot be changed, consequently,
%it can be used for reproducing the results of scientific
%experiments.
%Singularity takes snapshot, locks, and archives the developed application,
%which is known as Singularity image.
%It means that Singularity image is a single immutable file that can be moved around as
%any other file. This file can be checksummed, signed, and easily
%used for verification purposes. Singularity containers use Squashfs file format
%by default. It is read-only file system in Linux, which uses compression for files,
%inodes, and directories. However, Singularity also supports two other 
%formats i.e \textit{sandbox} format
%(which is just a chroot
%directory) and \textit{writable} format (the ext3 file system).
%While publishing experimental results, authors can also publish Singularity
%image along with its hash, which allow other researchers to verify results.
%\end{comment}
\subsection{Container Images}

We scan a total of 44 container images taken from two containerization frameworks
used in neuroscience: BIDS
apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}
Out of these 44 images, 26 were obtained from BIDS apps
\href{https://bids-apps.neuroimaging.io/apps/}{(https://bids-apps.neuroimaging.io/apps/)} 
and 18 from Boutiques. In fact, at the time of the study, BIDS apps has 27 images,
out of which one wasn't available on DockerHub. Boutiques has 49 images, listed using
Boutiques \texttt{bosh search} command,
however, only 23 unique were listed, out of which 3 couldn't be retrieved and 2
we decided to ignore as they were already included in BIDS apps. All the final 26 images
from BIDS apps are Docker images, whereas Boutiques contain 18 Docker images
and 6 Singularity images.

%Among the 27 BIDS apps \href{https://bids-apps.neuroimaging.io/apps/}
%{(https://bids-apps.neuroimaging.io/apps/)} available at the time of
%the study, we studied 26
%unique Docker images as one wasn't available on DockerHub. Among the 49
%Boutiques applications available at the time of the study, listed using
%Boutiques \texttt{bosh search} command, 23 unique container images were
%listed including 3 that couldn't be retrieved and 2 that were already
%included in BIDS apps. The resulting 18 images included 12 Docker images
%and 6 Singularity images.
%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

@@

We use four popular image scanners, namely Anchore~\cite{github_2019},
Vuls~\cite{future-architect_2019}, Clair-scanner~\cite{arminc_2019} and
Stools~\cite{stools}. Anchore, Vuls and Clair-scanner support Docker
images while Stools supports Singularity. Different vulnerabilities may be
reported if scanning experiments take place on different dates.
To avoid such discrepancies, we freeze the vulnerability
databases used by these scanners as of 2019-09-25, when we initiate our
experiments. This allows for a fair comparison between the scanners.

@@

Anchore is an end-to-end, open-source container security platform. It
is a static
scanning tool that analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
%\begin{comment}
%Anchore is a set of tools, which users can
%employ for scanning container images and applying custom policies to them.
%It provides visibility and transparency of the container environment.
%\end{comment}
Anchore Engine can be used in two ways: through Docker image or Anchore
Command Line Interface (CLI).
%\begin{comment}
%Anchore offers services in two ways: Anchore Engine and Anchore
%Command Line Interface (CLI). Anchore Engine is available as a Docker
%image, which is available on Docker Hub. Anchore Engine CLI provides
%command line interface in addition to Anchore Engine REST API. 
%\end{comment}
It can be
installed directly on the host and used to inspect images.
In our experiments, we use a Docker image in order to have access to Anchore Engine version 0.5.0 with the 
Anchore vulnerability database version 0.0.11.

Anchore compares package versions, which are present inside the
image, with the vulnerability database in order to flag vulnerabilities.
To get a vulnerability feed of various OS distribution, Anchore refers to
different sources, for instance, Ubuntu launchpad database to get
vulnerability data related to Ubuntu.

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
It offers both static and dynamic scanning. In our experiments, we use
it to dynamically scan containers.
Using a dynamic scanning technique, it offers
remote and local scans at the time of writing. The remote scan sets up only one machine to
which other target servers are connected via SSH. Local scan involves running
the scan on the target server itself. 
%Further, Vuls offer a fast scan, fast root scan,
%and deep scan mode.
%The Fast scan is performed without root privileges, whereas a fast root scan is
%performed with root privileges. The latter also uses checkrestart utility to 
%detect processes that are updated but not yet restarted because if they are not
%restarted, updates are not effective. Fast root scan also detects these
%processes. Both fast scan and fast root scan are performed offline without Internet
%access, and put almost no load on the scan target server. The Deep scan uses
%root privileges for scanning and is used to get a more detailed scan. It checks
%changelogs, which puts more load on the target server.

In our experiments, we use a Vuls Docker image having version 0.9.0. %with fast scan mode.
Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
It is worth noting that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
meaning that images with these distributions are hard to scan with Vuls.

\subsubsection{Clair-scanner}

Clair-scanner is a static vulnerability scanner for Docker containers.
%CoreOS originally created Clair, a static vulnerability scanner for containers. 
%The main goal of the
%tool is to provide a transparent look of container’s security. Clair scans container images in regular
%intervals, and stores metadata of vulnerabilities, after getting from configured
%set of sources. 
%Clair API can be used by clients to query its database to get
%the list of vulnerabilities that a particular image has. Clair sends a notification
%to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
%is a registry to store images privately, uses Clair internally as the security engine. 
%However, Clair does not 
%provide the facility for comparing
%the vulnerability list of a particular image against a whitelist of vulnerabilities that you
%want to ignore~\cite{arminc_2019}. 
%So, to remove
%that drawback, another tool, Clair Scanner can be used. 
It scans the image, prepares the list of
vulnerabilities, compares that list against a whitelist, and flags vulnerabilities
that are not present in the whitelist.
Clair-scanner utilizes the Ubuntu CVE tracker to obtain  Ubuntu vulnerability feed.
For that purpose, a Docker image is maintained that contains the Ubuntu CVE tracker database.
Whenever Ubuntu updates its database, this image is also updated with the required information.

In our experiments, we use a Docker image (arminc/clair-local-scan:v2.0.6) for scanning
and an another Docker image (arminc/clair-db:latest) for the vulnerability database, which was
last updated on 2019-09-18. We perform
scanning on 2019-09-25.

@@

Continuous Integration (CI) allows smaller code changes, fault isolations,
faster release date, etc. Two types of CI are commonly used : TravisCI and
CircleCI. The former targets open source projects that need to be tested in
different environments, whereas the latter targets smaller projects where
integration needs to be done as fast as possible. Stools uses CoreOS's Clair, which
is used for Docker images, in combination with CI to allow scanning of
Singularity images.
%Stools combines CoreOS's Clair with Continuous Integration (CI)
%for scanning Singularity images for vulnerabilities.
%Initially, Clair was intended to scan Docker images only. This tool does not fit well
%to scan Singularity images because of the different image formats.
%However, TravisCI and CircleCI are commonly used for testing code, and these
%services also offer running containers. Stools combined both these concepts.
It involves spinning a Clair container during testing and building a
Singularity image, and scanning it before the image is finalized.

In our experiments, we use a Docker image (\href{https://hub.docker.com/r/vanessa/stools-clair}{vanessa/stools-clair:v3.2.1})
following the steps mentioned in \href{https://github.com/singularityhub/stools}{Stools Github} for scanning
Singularity images.

@@

\section{Our Approach}

In this section, we present our approach, where we attempt the reduction
of security vulnerabilities in images by updating or
shrinking these images.

\subsection{Image Update Process}

If vulnerabilities exist in the container images, then our first approach
is to update these images in order to see the effects of such updates
on the vulnerabilities.
Updating an image involves updating all software packages that are
inside that image. We use a 
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/update/update.sh}{bash script} 
to update all images. That script checks the
package manager, which is present inside the image, and updates the image
accordingly. However, this action affects the reproducibility
of that image. For example, if a package is used by a scientist to conduct an experiment
and later that package is updated, other scientists want to reproduce initial results may actually
get different results due to updates.
%which means that the image cannot be used to verify the research
%findings of other scientists.
